---
title: 'Coursera: Causal Inferenence - Week 4'
output: html_document
---

### Prepare R
```{r}
install.packages("tableone")
install.packages("Matching")
install.packages("ipw")
install.packages("survey")
install.packages("MatchIt")
```

```{r}
library(tableone)
library(Matching)
library(ipw)
library(survey)
library(MatchIt)

data(lalonde)
```

### Inspect data
```{r}
str(lalonde)
```

### Task
Fit a propensity score model. Use a logistic regression model, where the outcome is treatment. Include the 8 confounding variables in the model as predictors, with no interaction terms or non-linear terms (such as squared terms). Obtain the propensity score for each subject. Next, obtain the inverse probability of treatment weights for each subject.

### Question 1
We use a logistic regression to calculate propensity scores:
```{r}
psmodel <- glm(treat ~ age + educ + 
                 black + hispan + married + nodegree +
                 re74 + re75,
               family = binomial(link = "logit"),
               data = lalonde)

min(psmodel$fitted.values)
max(psmodel$fitted.values)

ps <- predict(psmodel, type = "response" )
```

> glm.predict(type = "reponse"): the type of prediction required. The default is on the scale of the linear predictors; the alternative "response" is on the scale of the response variable. Thus for a default binomial model the default predictions are of log-odds (probabilities on logit scale) and type = "response" gives the predicted probabilities. The "terms" option returns a matrix giving the fitted values of each term in the model formula on the linear predictor scale.

### Question 2
Find the standardized differences for each confounder on the weighted (pseudo) population. What is the standardized difference for nodegree?

```{r}
weight <- ifelse(lalonde$treat==1, 1/ps, 1/(1-ps))

weighteddata <- svydesign(ids = ~1,
                          data = lalonde,
                          weights = weight)

xvars <- c("treat", "age", "educ", "black", "hispan", "married",          "nodegree", "re74", "re75", "re78")

weightedtable <- svyCreateTableOne(vars = xvars,
                                   strata = "treat",
                                   data = weighteddata,
                                   test = F)

print(weightedtable, smd = T)
```

### Question 3
Using IPTW, find the estimate and 95% confidence interval for the average causal effect. This can be obtained from svyglm
